I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-26 Paper/proofs.tex
proof Th 3

			\subsection{Preparation}

@@

			\begin{proof}	
				Fix an input vector $\boldsymbol{x}^0_J$.
				This also fixes the values in $D_J$.
				Consider the DNN $D'$ with input nodes $a_i\in I$, where all the 
				edges from $m \in D_J$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_J}(m)$) for $n$ (we summ all these bias for a neuron $n$).
				We denote $\val'$ values of nodes in this DNN $D'$.

@@

			\begin{corollary}
			For a node $b$ with $S(b)=1$:

@@

			\subsection{$\MILP_X$ is accurate}

			We denote by $X=B_{open}$, and consider $\MILP_{X}$.
			Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$.

@@

		We want to show that $\beta= \max(z)$. As the MILP abstraction is a sound over-approximation, it suffices to show that $\beta\leq \max (c)$.
		The case for $\alpha$ is similar.
		%We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:

\iffalse

@@

			From Lemma \ref{lem:main}, we already have that for the unique output node $z$, $$\UB(z)=\max(z).$$ This finish the proof of Theorem \ref{thm:2}.

			\subsubsection*{From weak to compensating}

>>>>

			\subsection{Proof of Theorem \ref{thm:2}}

@@

			\begin{proof}	
				Fix an input vector $\boldsymbol{x}^0_J$.
				This also fixes the values in $D_J$.
				Consider the DNN $D'$ with input nodes $a_i\in I$, where all the 
				edges from $m \in D_J$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_J}(m)$) for $n$ (we sum all these bias for a neuron $n$).
				We denote $\val'$ values of nodes in this DNN $D'$.

@@

			\begin{corollary}
				\label{corr:main}
			For a node $b$ with $S(b)=1$:

@@

			%\subsection{$\MILP_X$ is accurate}

			We denote by $X=B_{open}$, and consider $\MILP_{X}$.
			Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$. We want to show that $\beta= \max(z)$. 
			%As the MILP abstraction is a sound over-approximation, it suffices to show that %$\beta\leq \max (z)$.
			The case for $\alpha$ is similar.

@@

		%We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:

@@

We are now ready to finish the proof of Theorem \ref{thm:2}.

\begin{proof}
	We show that $\beta=\max(z)$.

	We fix the input vector $\vx^*_I$ for input $I$.
	This also fixes the values in $D_I$.
	Consider the DNN $D'$ with input nodes $J$, where all the 
	edges from $m \in D_I$ to $n$ are replaced by a bias (equals to the weight of the edge times the fix value $\val_{\boldsymbol{x}^0_I}(m)$) for $n$ (we sum all these bias for a neuron $n$).
	We denote $\val'$ values of nodes in this DNN $D'$.

	We have $\val'_{\boldsymbol{x}_J}(n)=\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n)$ 
	for every node $n$ of $D'$. All the ReLU nodes of $D'$ are in $X$, by definition of $X$.
Thus $\MILP_X$ will be fully accurate in $D'$. Let $\beta'$ denote its upper bound.
We have $\beta'=\max_{\vx{_J}} (\val'_{\vx_{J}}(z)) = 
\Val_{\boldsymbol{x}^*_I,\boldsymbol{x}_J}(n) = \max(z)$ by Corrolary \ref{corr:main}.
Now, in $D$, $\MILP_X$ will use simple LP on $D_I$, which suffices to get the upper bound $\val_{\vx^*_I}(n)=\max(n)$ for all $n$ in $D_I$ and the values will be pushed as bias in $D'$. Therefore, $\beta=\beta'=\max(z)$.

The case for $\alpha=min(z)$ is similar. \qed

\subsection{From weak to compensating}
